\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-21 paper2015asml.tex
abstract

This electronic document is a ÒliveÓ template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.

\end{abstract}

>>>>

Co-robots, i.e. robots that need to work close to people, will need to account for the preferences and expectations of their human 
co-workers in executing motions or actions. Consistent, legible and predictable motions are a key factor in making humans comfortable 
around robots. In this work, we take a first step towards designing motions that are more acceptable to human co-workers by asking 
people to rate robot motions generated in a variety of environments. We compute a set of features for each trajectory and use the features 
and associated rating to derive a quality score that represents how well the human observers liked the trajectory. We present an 
analysis of the dataset that we have collected, highlighting the features that dominate the trajectories that people prefer. We also 
present a classifier that will return the quality score for a given trajectory. Finally, we discuss how a data-driven approach using the 
results of this analysis can be used to help design better plans that are more acceptable to people. 
\end{abstract}
